### 2022-08-26 README.Rmd
added DOI badge to readme

[![R-CMD-check](https://github.com/joseph-palmer/wagglefit/actions/workflows/check-standard.yaml/badge.svg)](https://github.com/joseph-palmer/wagglefit/actions/workflows/check-standard.yaml)
[![lint](https://github.com/joseph-palmer/wagglefit/actions/workflows/lint.yaml/badge.svg)](https://github.com/joseph-palmer/wagglefit/actions/workflows/lint.yaml)
[![pkgdown](https://github.com/joseph-palmer/wagglefit/actions/workflows/pkgdown.yaml/badge.svg)](https://github.com/joseph-palmer/wagglefit/actions/workflows/pkgdown.yaml)
[![test-coverage](https://github.com/joseph-palmer/wagglefit/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/joseph-palmer/wagglefit/actions/workflows/test-coverage.yaml)

>>>>

[![R-CMD-check](https://github.com/joseph-palmer/wagglefit/actions/workflows/check-standard.yaml/badge.svg)](https://github.com/joseph-palmer/wagglefit/actions/workflows/check-standard.yaml)
[![lint](https://github.com/joseph-palmer/wagglefit/actions/workflows/lint.yaml/badge.svg)](https://github.com/joseph-palmer/wagglefit/actions/workflows/lint.yaml)
[![pkgdown](https://github.com/joseph-palmer/wagglefit/actions/workflows/pkgdown.yaml/badge.svg)](https://github.com/joseph-palmer/wagglefit/actions/workflows/pkgdown.yaml)
[![test-coverage](https://github.com/joseph-palmer/wagglefit/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/joseph-palmer/wagglefit/actions/workflows/test-coverage.yaml)
[![DOI](https://zenodo.org/badge/353413244.svg)](https://zenodo.org/badge/latestdoi/353413244)
